
\section{Conclusion}
\label{sec:conclusion}


In this paper, we proposed an original causal broadcast protocol that removes
the last linear upper bound in terms of number of processes that ever broadcast
a message that remained on local space complexity. This approach only uses
buffers of messages that grow and shrink when processes add new neighbors. They
eventually become empty when the system becomes static. To achieve this, our
approach only uses small control messages of constant size. The number of
control messages depends on the overlay network. Using routing strategies, this
number remains small, hence generated traffic overhead remains small. This
advantageous tradeoff makes causal broadcast a lightweight and efficient
middleware for group communication in distributed systems. This advantageous
tradeoff even makes \RPCBROADCAST a lightweight and efficient implementation
for reliable broadcast. As consequence, causal broadcast and reliable broadcast
can run in large and dynamic systems even on most humble devices such as
Raspberry Pi’s.

As future work, we plan to investigate on ways to retrieve the partial order of
messages out of \RPCBROADCAST. Using \RPCBROADCAST, each process experiences a
flatten version of the partial order. However, several applications (\REF)
require more than causal order, they also need to identify concurrent
messages. \RPCBROADCAST discards a lot of information by ignoring multiple
receipts. Analyzing the receipt order could provide insight on the partial
order. Instead of using vector clocks the cost of which increases with the
number of processes that ever broadcast, the cost would depend on the actual
concurrency of the system.

% Analysing the receipt order of messages in \RPCBROADCAST could provide
% additional information on the upstream.


% State-of-the-art relies on vector clocks to capture concurrency. The size of
% vectors increases linearly with the number of processes that ever broadcast. In
% other terms, scenarios without concurrent messages still pay the full price of
% concurrency tracking. By analysing the order of receipts in \RPCBROADCAST, we
% want to retrieve the partial order at limited cost.


%\TODO{Moar.}


%%% Local Variables:
%%% mode: latex
%%% TeX-master: "../paper"
%%% End:
